Applied Measure Theory for Probabilistic Modeling

### 2022-05-20 paper/paper.tex
edits

>>>>

Just as \verb|logdensity_def(μ,x)| defines the log-density relative to the default base measure, it's often useful to be able to define the log-density between two measures that are given explicitly. For this, we have the three-argument \verb|logdensity_def(μ,ν,x)|.

Though this three-argument form is available as a primitive, it would be intractable to use it to define log-densities for every pair of measures. Instead, \verb|basemeasure| forms a \emph{forest} (a collection of trees, with $μ \rightarrow \nu$ if \verb|ν=basemeasure(μ)|). The three-argument \verb|logdensity_def| connects trees to form a graph. For any two measures, \verb|MeasureTheory| can traverse this graph at compile time to determine how to compute the log-density.
